### 2021-12-13 input/proposal.tex
reworked figures mostly

\TODO{$FB \subseteq FB+$}.

\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \TODO{\wedge \textup{D}} \implies \textup{DCP}$]
  A protocol guarantees dynamic consistent partitioning if it
  implements forwarding of best up-to-date messages with echos,
  forwarding of staleness messages downstream, and detection of
  possible blocking of staleness notifications.
\end{theorem}

@@

In Edge infrastructures comprising tens of thousands of autonomous
systems~\cite{nur2018crossas}, only a small subset of autonomous
systems needs logical partitioning. At any time, an autonomous system
start logical partitioning when a \process from this network becomes a
source.  Then every \process from this network belongs to the
partition of its closest source not only from their own network but
that of adjacent networks that started logical partitioning as well.
At any time, an autonomous system stops logical partitioning when the
last source from this network revokes its status of
source. Eventually, all nodes from this network do not belong to any
partition and the generated traffic stops.

>>>>

\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \implies \textup{DCP}$]
  A protocol guarantees dynamic consistent partitioning if it
  implements forwarding of best up-to-date messages with echos,
  forwarding of staleness messages downstream, and the detection of
  possible blocking triggers the forwarding of staleness notifications
  downstream.
\end{theorem}

@@

\TODO{In Edge infrastructures comprising tens of thousands of autonomous
systems~\cite{nur2018crossas}, only a small subset of autonomous
systems needs logical partitioning. At any time, an autonomous system
start logical partitioning when a \process from this network becomes a
source.  Then every \process from this network belongs to the
partition of its closest source not only from their own network but
that of adjacent networks that started logical partitioning as well.
At any time, an autonomous system stops logical partitioning when the
last source from this network revokes its status of
source. Eventually, all nodes from this network do not belong to any
partition and the generated traffic stops.}

\TODO{Further scale, follow up of motivations.}
